### 2018-11-12 paper.tex
add screenshot examples

\algorithmspace
\begin{algorithm}
  \DontPrintSemicolon
%  \LinesNumbered
  \KwIn{events}
  \BlankLine
  \tcp{Initialization}
  $beachline$ := the line equidistant between the event and the event\;
  $closeEventPoints$ := the set of all close \;
  \While{events > 0 and exists events in sweepline path}{
  	let $e$ := the next event\;
    \If{$e$ is close event}{
    	\If{$e$ is live}{
    	  update arch node points\;
    	  remove $e.archNode$ from the $beachline$\;
% 		  \ForEach{$ev$ in events}{
% 		  	\If{$ev.y$ less than $e.y$ - \varepsilon}{
% 		  		add $ev$ to events\;
% 		  		\If{$ev$ is close event}{
% 		  			add $ev$ to $closeEventPoints$\;
% 		  		}
% 		  	}
% 		  }
		}
   	}
    \Else{
   	  \tcp{Site event}
   	  add $e$ to the $beachline$
%   	  \ForEach{$ev$ in events}{
%   	  	\If{$ev.y$ less than $e.y$ - \varepsilon}{
%   	  		add $ev$ to events
%   	  		 \If{$ev$ is close event}{
%   	  		 	add $ev$ to $closeEventPoints$
%   	  		 }
%   	  	}
%   	  }
    }
  }
\caption{COMPUTE\_DISTANCES}
\label{alg:compute-distances}
\end{algorithm}
\algorithmspace

@@

\begin{figure}
  \centering
  \subfloat[][]{
    \label{fig:wavefront5}
    \includegraphics[width=0.32\columnwidth]{filler.png} }
  \subfloat[][]{
    \label{fig:wavefront6}
    \includegraphics[width=0.32\columnwidth]{filler.png} }
  \subfloat[][]{
    \label{fig:wavefront7}
    \includegraphics[width=0.32\columnwidth]{filler.png} } \\
  \subfloat[][]{
    \label{fig:wavefront2}
    \includegraphics[width=0.32\columnwidth]{filler.png} }
  \subfloat[][]{
    \label{fig:wavefront4}
    \includegraphics[width=0.32\columnwidth]{filler.png} }
  \subfloat[][]{
    \label{fig:wavefront6-gvd}
    \includegraphics[width=0.32\columnwidth]{filler.png} }
  \caption{Wavefront expansion.
    \protect\subref{fig:wavefront5} Portions of the surfaces of two objects. Assign every nonempty vertex an exact closest point and add the vertex to the wavefront priority queue.
    \protect\subref{fig:wavefront6} Pop the top priority vertex (dotted circle) and push its closest point to its neighbors (circle).
    \protect\subref{fig:wavefront7} Next iteration.
    \protect\subref{fig:wavefront2} Initialized wavefront (as in \protect\subref{fig:wavefront6}).
    \protect\subref{fig:wavefront4} Expanded wavefront.  Green lines connect quadtree vertices to computed closest points.
    \protect\subref{fig:wavefront6-gvd} The GVD is shown in red.
  }
  \label{fig:wavefront}
\end{figure}

>>>>

\algorithmspace
\begin{algorithm}
  \DontPrintSemicolon
%  \LinesNumbered
  \KwIn{events}
  \BlankLine
  \tcp{Initialization}
  $beachline$ := the set of arc nodes\;
  $closeEventPoints$ := the set of all close events\;
  $events$ := a list of sorted points or sites\;
  \While{$events$ > 0}{
  	let $e$ := the next event in $events$\;
  	move the sweepline to include point $e$\;

    \If{$e$ is a close event}{
    	\If{$e$ is live}{
    	  update the associated arc node to close on point $e$\;
    	  remove the arc node from the $beachline$ and return $newEvents$\;

    	  \ForEach{$ev$ in $newEvents$}{
    	  	\If {$ev$ is below $e$}{
    	  		add $ev$ to $events$\;
    	  		\If{$ev$ is a close event}{
    	  			add $ev$ to $closeEventPoints$
    	  		}
    	  	}
    	  }

		}
   	}
    \Else{
   	  \tcp{Site event}
   	  add $e$ to the $beachline$ and return $newEvents$
   	   \ForEach{$ev$ in $newEvents$}{
   	  	\If {$ev$ is below $e$}{
   	  		add $ev$ to $events$\;
   	  		\If{$ev$ is a close event}{
   	  			add $ev$ to $closeEventPoints$
   	  		}
   	  	}
   	  }
    }
  }
\caption{COMPUTE\_DISTANCES}
\label{alg:compute-distances}
\end{algorithm}
\algorithmspace

@@

\begin{figure}
  \centering
  \subfloat[][]{
    \label{fig:sweepA}
    \includegraphics[width=0.32\columnwidth]{fig1_a.png} }
  \subfloat[][]{
    \label{fig:sweepB}
    \includegraphics[width=0.32\columnwidth]{fig1_b.png} }
  \subfloat[][]{
    \label{fig:sweepC}
    \includegraphics[width=0.32\columnwidth]{fig1_c.png} } \\
  \subfloat[][]{
    \label{fig:sweepD}
    \includegraphics[width=0.32\columnwidth]{fig1_d.png} }
  \subfloat[][]{
    \label{fig:sweepE}
    \includegraphics[width=0.32\columnwidth]{fig1_e.png} }
  \subfloat[][]{
    \label{fig:sweepF}
    \includegraphics[width=0.32\columnwidth]{fig1_f.png} }
  \caption{Sweepline Algorithm
    \protect\subref{fig:sweepA} Place Explanation Here
    \protect\subref{fig:sweepB} Place Explanation Here
    \protect\subref{fig:sweepC} Place Explanation Here
    \protect\subref{fig:sweepD}  %(as in \protect\subref{fig:wavefront6}).
    \protect\subref{fig:sweepE} Place Explanation Here
    \protect\subref{fig:sweepF} Place Explanation Here
  }
  \label{fig:wavefront}
\end{figure}
